Practical Hilbert space approximate Bayesian Gaussian processes for probabilistic programming

### 2020-04-22 Paper/manuscript_v2/manuscript_07_01.tex
Minor edits to sec 5.1

In this experiment, we analyze a synthetic dataset with $n = 250$ observations, where the true data generating process is a Gaussian process with additive noise. The data points are simulated from the model $y_i = f(x_i) + \epsilon_i$, where $f$ is a sample from a Gaussian process using the Mat{\'e}rn($\nu$=3/2) covariance function with marginal variance $\alpha=1$ and lengthscale $\ell=0.15$ at inputs values $\bm{x}=(x_1,x_2,\dots,x_n)$ with $x_i \in [-1,1]$. $\epsilon_i$ is additive Gaussian noise with standard deviation $\sigma=0.2$. From this synthetic dataset, $155$ data points are used as sample data, $45$ as interpolation out-of-sample test data, and $50$ as extrapolation out-of-sample test data.

@@

The joint posterior parameter distributions are estimated from the sampling data using dynamic HMC algorithm implemented in Stan \citep{carpenter2017stan,betancourt2017conceptual}. A $\mathrm{Gamma}(1,1)$ prior distribution has been used for both observation noise $\sigma$ and covariance function marginal variance $\alpha$, and a $\mathrm{Gamma}(3.75,25)$ prior distribution for lengthscale $\ell$, either in exact GP or HSGP models.

>>>>

In this experiment, we analyze a synthetic dataset with $n = 250$ observations, where the true data generating process is a Gaussian process with additive noise. The data points are simulated from the model $y_i = f(x_i) + \epsilon_i$, where $f$ is a sample from a Gaussian process using the Mat{\'e}rn($\nu$=3/2) covariance function with marginal variance $\alpha=1$ and lengthscale $\ell=0.15$ at inputs values $\bm{x}=(x_1,x_2,\dots,x_n)$ with $x_i \in [-1,1]$. $\epsilon_i$ is additive Gaussian noise with standard deviation $\sigma=0.2$. We split the dataset into three parts: $155$ data points are used for fitting the model (training set), $45$ data ponts are used for the interpolation test set, and the remaining $50$ data points are used for the extrapolation test set.

@@

The joint posterior parameter distributions are estimated by sampling using the dynamic HMC algorithm implemented in Stan \citep{carpenter2017stan,betancourt2017conceptual}. A $\mathrm{Gamma}(1,1)$ prior distribution has been used for both observation noise $\sigma$ and covariance function marginal variance $\alpha$, and a $\mathrm{Gamma}(3.75,25)$ prior distribution for lengthscale $\ell$. We use the same prior distributions for the exact GP model as for the HSGP models.
